---
title: "Case Study 2"
author: "Lizzy Sterling and Casey Martinez"
date: "12/06/2017"
output: rmarkdown::github_document
---
# Project Overview  
Now that we have completed data collection, which can be found in `Procrastination.csv`, it is now time to conduct analysis. As we discussed, there are a few variables in particular that are worth looking at. These include age, annual income, and country of origin.  
## Key Questions  


### Libraries used  
library(XML)  
library(rvest)  
library(dplyr)  
library(ggplot2)  
library(ggthemes)  
library(plyr)  
library(knitr)  
```{r, echo=TRUE, include=FALSE}
if (!require(XML)) install.packages('XML')
library(XML)
library(rvest)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plyr)
library(knitr) #kable function
```

```{r, echo=TRUE}
knitr::opts_knit$set(root.dir = '/Users/lizzysterling/Desktop/CaseStudy2/Analysis/Data')
```
## Data Cleaning
Although we finished data collection, there is still some tidying to do. As you can see, it is a rather large data set, so we need to go back through and make sure that all of the entries are ready for analysis.  
```{r, echo=TRUE, fig.width=15,fig.height=5}
#2A
#setwd("Data")
Procrastination <- read.csv("Procrastination.csv", header=TRUE, stringsAsFactors=FALSE)
dim <- data.frame(nrow(Procrastination),ncol(Procrastination))
colnames(dim) <- c("Number of Rows", "Number of Columns")
kable(dim)
```  
   
   
In order to make the data set human-readable, we need to change the column names so that they make more sense. 
*You can reference the README.md file in the `Data` folder for further descriptions of these columns (columns 15 to 61 in particular)*
```{r, echo=TRUE}
#2B
names(Procrastination) <- c("Age", "Gender", "Kids", "Education", "WorkStatus", "AnnualIncome", "Occupation", "OccupationYears", "OccupationMonths", "CommunitySize", "CountryOfResidence", "MaritalStatus", "NumberSons", "NumberDaughters", "DP1", "DP2", "DP3", "DP4", "DP5", "AIP1", "AIP2", "AIP3", "AIP4", "AIP5", "AIP6", "AIP7", "AIP8", "AIP9", "AIP10", "AIP11", "AIP12", "AIP13", "AIP14", "AIP15", "GP1", "GP2", "GP3", "GP4", "GP5", "GP6", "GP7", "GP8", "GP9", "GP10", "GP11", "GP12", "GP13", "GP14", "GP15", "GP16", "GP17", "GP18", "GP19", "GP20", "SWLS1", "SWLS2", "SWLS3", "SWLS4", "SWLS5", "P1", "P2")
```
Now that we have human-readable column names, let's take a look at the data:  
```{r, echo=TRUE}
head(Procrastination)
```

We need to change the `Age` column so that they are in whole numbers. 
```{r, echo=TRUE}
Procrastination$Age <- as.integer(Procrastination$Age)
```
We also need to make the values of `OccupationYears` to integers and then determine which years do not makes sense.  
```{r, echo=TRUE, fig.width=15, fig.height=5}
#2C
Procrastination$OccupationYears <- as.integer(Procrastination$OccupationYears)
OccupationYears <- data.frame(unique(Procrastination$OccupationYears))
colnames(OccupationYears) <- "OccupationYears"
kable(OccupationYears)
```
We are going to change all of the 999 entries to NAs, because this is likely a mistake.  
```{r, echo=TRUE}
Procrastination[grep("999", Procrastination$OccupationYears), "OccupationYears"] <- ""
```

Now looking at the `NumberSons` column, we noticed that some of the entries are `Male` and `Female` rather than integer values. 
```{r, echo=TRUE, fig.width=15, fig.height=5}
NumberSons <- data.frame(unique(Procrastination$NumberSons))
colnames(NumberSons) <- "Number of Sons"
kable(NumberSons)
```  
  
  
We know that in this column, `Male`= 1 Son and `Female` = 2 Sons. Therefore, we need to change each Male and Female entry to their corresponding numbers so that they can be counted correctly.  
```{r, echo=TRUE}
Procrastination[grep("^Male.*", Procrastination$NumberSons),"NumberSons"] <- rep(1, length(Procrastination[grep("^Male.*", Procrastination$NumberSons),"NumberSons"]))

Procrastination[grep("^Female.*", Procrastination$NumberSons),"NumberSons"] <- rep(2, length(Procrastination[grep("^Female.*", Procrastination$NumberSons),"NumberSons"]))

```  
  
  
In our `CountryOfResidence` column, we only want values that are really countries. 
```{r, echo=TRUE}
Country <- data.frame(unique(Procrastination$CountryOfResidence))
colnames(Country) <- "Number of Sons"
kable(Country)
```
Because 0 is not a country of residence, we need to change it to a NA.  
```{r, echo=TRUE}
Procrastination[grep("0", Procrastination$CountryOfResidence), "CountryOfResidence"] <- ""
```
Looking at `Occupation`, we want to get rid of values that arent really jobs, as well as combine like-jobs together.  
```{r, echo=TRUE}
Occupation <- data.frame(unique(Procrastination$Occupation))
colnames(Occupation) <- "Occupation"
kable(Occupation)
```

First, we notice that `please specify` and `0` are not occupations, we can get rid of them.  
```{r, echo=TRUE}
Procrastination[grep("0", Procrastination$Occupation), "Occupation"] <- ""
Procrastination[grep("please specify", Procrastination$Occupation), "Occupation"] <- ""
```
Because this was a fill in the blank type question, there are many answers that could be grouped with others. We can group these occupations together so that we can get accurate counts. Some examples include entries that include `Teachers` and entries that include `Computer`.  
```{r, echo=TRUE}
Procrastination[(grep("teacher", Procrastination$Occupation)), "Occupation"] <- "Teacher"
Procrastination[(grep("Computer", Procrastination$Occupation)), "Occupation"] <- "Computers"
```

Now that all of the columns are clean, we need to make sure they are of the correct data types.  
```{r, echo=TRUE}
kable(sapply(Procrastination, class), col.names="Class Type")
```  
  
We want to change both the `OccupationYears` and `NumberSons` into numeric values.  
```{r, echo=TRUE}
Procrastination$OccupationYears <- as.numeric(Procrastination$OccupationYears)
Procrastination$NumberSons <- as.integer(Procrastination$NumberSons)
```

Although all of this is interesting, the procrastination scales are what we are really interested in, so we are going to take the means of each row to create mean scores for each individual. These new rows are `DPmean`, `AIPmean`, `GPmean`, and `SWLSmean`.  
```{r, echo=TRUE}
Procrastination$DPmean <- rowMeans(Procrastination[15:19],na.rm = TRUE)
Procrastination$AIPmean <- rowMeans(Procrastination[20:34],na.rm = TRUE)
Procrastination$GPmean <- rowMeans(Procrastination[35:54],na.rm = TRUE)
Procrastination$SWLSmean <- rowMeans(Procrastination[55:59],na.rm = TRUE)
```

### Scraping the HDI Data  
Now that `Procrastination.csv` is tidy, we noticed that there are many countries included in the data set. We thought, wouldn't it be interesting to see how the Human Development Index of each country relates to its respective rate of procrastination.  
To do this, we took data found on this website https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries.  
```{r, echo=TRUE}
#3A
link = "https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries"
doc <- read_html(link) 
node <- html_nodes(doc,"table")
tables <- html_table(node, fill = TRUE)
```

From this data, we needed to create data frames from the tables collected.  
```{r, echo=TRUE}
df1 <- as.data.frame(tables[4]) #Very High Human Development1
df2 <- as.data.frame(tables[5]) #Very High Human Development2
df3 <- as.data.frame(tables[7]) #High Human Development1
df4 <- as.data.frame(tables[8]) #High Human Development2
df5 <- as.data.frame(tables[10]) #Medium Human Development1
df6 <- as.data.frame(tables[11]) #Medium Human Development2
df7 <- as.data.frame(tables[13]) #Low Human Development1
df8 <- as.data.frame(tables[14]) #Low Human Development2
```

```{r, echo=TRUE}
#3B
df1 <- df1[-1,3:4]
colnames(df1) <- c('Country','HDI')
df1$Category <- "Very High"

df2 <- df2[-1,3:4]
colnames(df2) <- c('Country','HDI')
df2$Category <- "Very High"

df3 <- df3[-1,3:4]
colnames(df3) <- c('Country','HDI')
df3$Category <- "High"

df4 <- df4[-1,3:4]
colnames(df4) <- c('Country','HDI')
df4$Category <- "High"

df5 <- df5[-1,3:4]
colnames(df5) <- c('Country','HDI')
df5$Category <- "Medium"

df6 <- df6[-1,3:4]
colnames(df6) <- c('Country','HDI')
df6$Category <- "Medium"

df7 <- df7[-1,3:4]
colnames(df7) <- c('Country','HDI')
df7$Category <- "Low"

df8 <- df8[-1,3:4]
colnames(df8) <- c('Country','HDI')
df8$Category <- "Low"
```

Now that we have the data organized, we can combine them together and create a new csv `HumanDevelopmentIndex.csv`
```{r, echo=TRUE}
df <- rbind(df1,df2,df3,df4,df5,df6,df7,df8)
write.csv(df, "HumanDevelopmentIndex.csv",row.names = FALSE)
```
## Analysis
Now that the scraped data is saved into a file in the data folder, we need to combine it with our original data into a new variable `Pro`.
```{r, echo=TRUE}
#3C
HDI <- read.csv("HumanDevelopmentIndex.csv", header=TRUE)
Pro <- merge(x = Procrastination,y = HDI, by.x = 'CountryOfResidence', by.y = "Country")
```
### Adult Analysis  
From here-on-out, we only want to look at adult observations, so we are going to remove participants who are under 18. This new variable is `ProAdult` and this is the set we are going to be using for the rest of the analysis.  
```{r, echo=TRUE}
#4A
ProAdult <- Pro[Pro$Age > 18,]
```

The variables that we are most interested in are age, income, HDI, and the procrastination scale scores. We started by getting their summary statistics. 
```{r, echo=TRUE}
#4B
row <- c("Minimum", "First Quartile", "Median", "Mean", "3rd Quartile", "Maximum", "NA's")

AgeSummary <- summary(ProAdult$Age)
IncomeSummary <- summary(ProAdult$AnnualIncome)
HDISummary <- summary(ProAdult$HDI)
DPSummary <- summary(ProAdult$DPmean)
GPSummary <- summary(ProAdult$GPmean)
AIPSummary <- summary(ProAdult$AIPmean)
SWLSSummary <- summary(ProAdult$SWLSmean)

kable(matrix(AgeSummary, dimnames = list(row,"Statistics for Age")), digits = 0, row.names=TRUE) 
kable(matrix(IncomeSummary, dimnames = list(row,"Statistics for Annual Income")), digits = 2, row.names=TRUE)
kable(matrix(HDISummary, dimnames = list(row,"Statistics for Human Development Index")), digits = 4, row.names=TRUE)
kable(matrix(DPSummary, dimnames = list(row,"Statistics for Decisional Procrastination")), digits = 4, row.names=TRUE)
kable(matrix(GPSummary, dimnames = list(row,"Statistics for Generalized Procastination")), digits = 4, row.names=TRUE)
kable(matrix(AIPSummary, dimnames = list(row,"Statistics for Adult Procrastination")), digits = 4, row.names=TRUE)
kable(matrix(SWLSSummary, dimnames = list(row,"Statistics for Satisfaction with Life Scale")), digits = 4, row.names=TRUE)

```

We are most interested in age and income, so we graphed them to see their distributions.  

From the age distribution, you can see that there were more younger participants than older participants. Although the distribution is somewhat normal, there is definitely a stronger tendency towards the younger individuals.  
```{r, echo=TRUE}
ggplot(ProAdult, aes(Age)) +
  geom_histogram() + 
  labs(x="\nAge",y="Frequency\n") + 
  ggtitle("Age of Procrastinators")
```

From the income histogram, you can see that there is a right skew with the majority of individuals earning less than $50,000 a year.  
```{r, echo=TRUE}
ggplot(ProAdult, aes(AnnualIncome)) +
  geom_histogram() + 
  labs(x="\nIncome",y="Frequency\n") + 
  ggtitle("Annual Income of Adult Procrastinators")
```

In addition to these variables, we are going to look at gender, work status, and occupation.  
```{r, echo=TRUE}
#4C
GenderTable <- table(ProAdult$Gender)

WorkStatusTable <- table(ProAdult$WorkStatus)

OccupationTable <- table(ProAdult$Occupation)

#These don't look very pretty in the mark down file
ProAdult %>%  
  count_(GenderTable, sort=TRUE)

ProAdult %>%
  count_(WorkStatusTable, sort=TRUE)

ProAdult %>% 
  count_(OccupationTable, sort=TRUE)
```
We are going to look at how many people per country took our survey.  
```{r, echo=TRUE}
#4D
CountryTable <- table(ProAdult$CountryOfResidence)
ProAdult %>% 
  count_(CountryTable, sort=TRUE)
```

We thought it would be interesting to know how many people have an accurate view of whether or not they are a procrastinator. We did this by finding out how many people who reported to yes, I am a procrastinator also reported yes, others think I am a procrastinator and vice versa.  
```{r, echo=TRUE}
#4e
A <- table(ProAdult$P1,ProAdult$P2)
A[-1,-1]
A[-1,-c(1,2,3)]
#could use some labels
```

After this, we are very interested in which nations have the highest reports of procrastination.  
```{r, echo=TRUE}
#5B
df3 <- aggregate(DPmean ~ CountryOfResidence + Category, data = ProAdult, mean)
df3 <- head(df3[order(df3$DPmean, decreasing = TRUE),], n=15)

ggplot(data = df3, aes(y = DPmean,x = reorder(CountryOfResidence, DPmean))) + 
  geom_col(aes(fill = Category)) +
  coord_flip() +
  labs(x = 'Country',y = 'DP Mean',title = 'Top 15 Nations Average Procrastination Scores') +
  theme_economist() +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.text.x = element_text(size=7))
```

```{r, echo=TRUE}
#5C
df4 <- aggregate(GPmean ~ CountryOfResidence + Category, data = ProAdult, mean)
df4 <- head(df4[order(df4$GPmean, decreasing = TRUE),], n=15)

ggplot(data = df4, aes(y = GPmean,x = reorder(CountryOfResidence, GPmean))) + 
  geom_col(aes(fill = Category)) +
  coord_flip() +
  labs(x = 'Country',y = 'DP Mean',title = 'Top 15 Nations Average Procrastination Scores') +
  theme_economist() +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.text.x = element_text(size=7))
```

We want to look at how age and income are related to see if there is a pattern.  Although there is significance (insert p-value), the r^2 is not very high, so a relationship cannot be assumed. This discrepency may be attributed to the high number of degrees of freedom. 
```{r, echo=TRUE}
#Question 5d
ggplot(ProAdult, aes(Age, AnnualIncome)) + 
  geom_point(aes(fill=Gender),stat="identity")
```

```{r, echo=TRUE}
#5E
ggplot(ProAdult, aes(SWLSmean, HDI)) + 
  geom_point(aes(fill=Gender), stat="identity")
```
```{r, echo=TRUE}
ggplot(ProAdult, aes(SWLSmean, Category)) + 
  geom_point(aes(fill=Gender), stat="identity")
```
Combine 3A, 3B, 3C, 5B and 5C and output into a csv
```{r, echo=TRUE}

```

## Conclusion  
